Verifying Demonstrations

### 2019-06-28 paper/DB-anon-cred.tex
Prepares remaining security proof (WIP)

The intuition behind the protocol security is as follows.
The prover must know the responses for all challenges to successfully pass the 
\ac{DB} phase.
The reason for having several challenges but only one random nonce is that 
knowing at least two responses means learning \(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem in the next section.)
However, the properties of \(\UWBPR\) ensures \ac{DBMF} resistance.

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack.
Thus, any relaying will be detected.
The adversary could guess the challenge bit \(b\), request \(s_b\) from the 
prover and guess \(s_{1-b}\).
The success probability of this is \(\frac{1}{2} + \frac{1}{q}\) per round, 
thus \((\frac{q + 2}{2q})^n\) in total.

@@

Finally, it follows from the original Schnorr protocol that this is still 
\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
security parameter \(\lambda\) and repeat the protocol \(n\) times.

\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

\subsection{Achieving \acl{DBDF} and \acl{DBTF} resistance}

\Acl{DB} protocols requires hardware implementations.
We will use a trusted hardware implementation to overcome the limitation of 
\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
This will also require \iac{PKI} to overcome the shared-key requirement and for 
a verifier to be able verify the hardware of a prover.

>>>>

The intuition behind the protocol security is as follows.
The prover must know the responses for all challenges to successfully pass the 
\ac{DB} phase.
The reason for having several challenges but only one random nonce is that 
knowing at least two responses means learning the secret~\(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem in the next section.)
However, the properties of \(\UWBPR\) and the unpredictability of the 
challenges ensures \ac{DBMF} resistance.

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
Thus, any relaying will be detected.
The adversary could guess the challenge chosen, \(i\), request \(s_i\) from the 
prover and guess \(s_j\) for \(i\neq j\).
The success probability of this is \(\frac{1}{k} + \frac{k}{q}\) per round, 
thus \((\frac{q + k}{kq})^n\) in total.

@@

\NewAlgorithm{\adv}{A}

\begin{proof}[\acs*{DBTF} resistance]
  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
  provers help with non-negligible advantage~\(\epsilon\), \ie the success 
  probability is \(\frac{1}{2}+\epsilon\).
  There is chance that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
  Thus, there is some case for which \(\adv\) knows both responses.
  In that case \(\adv\) can simply compute the secret and impersonate with 
  probability \(1\) forever.
\end{proof}

\begin{proof}[\acs*{DBDH} resistance]
  The adversary must find a collision of challenges for the honest provers 
  challenges, so that the verifying equation holds at the end.
\end{proof}

\subsection{Achieving \acl{DBDF} resistance}

\Acl{DB} protocols requires hardware implementations.
We will use a trusted hardware implementation to overcome the limitation of 
\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which simultaneously proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement holds, and
\item that that knowledge is within proximity.
\end{enumerate*}
